Object Naming in Language and Vision: A Survey and a New Dataset

### 2019-11-29 papers/LREC2020/background.tex
more discussion in sec 3

Seminal work by \newcite{rosch1976basic} inspired a taxonomic view of object naming, in which names exhibit a preferred level of specificity or abstraction called the ``entry-level'' \cite{jolicoeur1984pictures}. 
This typically corresponds to an intermediate level of specificity (basic level,\ e.g., \refexp{bird}, \refexp{car}), as opposed to more generic (super-ordinate,\ e.g., \refexp{animal}, \refexp{vehicle}) or more specific categories (sub-ordinate,\ e.g., \refexp{sparrow}, \refexp{convertible}).
However, less prototypical members of basic level categories tend to be instead identified with sub-ordinate categories (e.g., a penguin is typically called \refexp{penguin} and not \refexp{bird}; \newcite{jolicoeur1984pictures}). 
%This out-of-context preference towards a certain taxonomic level is often referred to as \textbf{lexical availability}. 
While the traditional notion of entry-level categories suggests that objects tend to be named by a \refexp{single} preferred concept, research on pragmatics has found that speakers are flexible in their choice of the level of specificity \cite{olson1970language,rohde2012communicating,graf2016animal}.
%Scenarios where multiple objects (of the same category) are present induce a pressure for generating names which uniquely identify the target \cite{olson1970language}, such that sub-level names can be systematically elicited in these cases \cite{rohde2012communicating,graf2016animal}.
For example, in presence of more than one dog, the name \textsl{dog} is ambiguous and a sub-ordinate category (e.g., \textsl{rottweiler}, \textsl{beagle}) is potentially preferred by speakers.
%, though additional factors such as cost or saliency also come into play \cite{graf2016animal,clark1983common}.
The purely taxonomic view has been criticized in more recent work on object organization, which found that many objects of our daily lifes are part of multiple category systems at the same time \cite{ross1999food,SHAFTO20111}. 
This \textit{cross-classification} occurs, for instance, with food categories which can be taxonomy-based (e.g.\ \refexp{meat, vegetable}) or script-based (e.g.\  \refexp{breakfast, snack}).
We provide tentative evidence that cross-classification is indeed relevant for naming variation, and that the taxonomic axis is not the main parameter that accounts for variation in our data.

@@

\begin{table*}[htb]
  \centering
  \begin{tabular}{lrrrrr}
    \toprule
    &   RefCoco/+  &  Flickr30kE &           VG &      VGmn &        MN \\
    \midrule
    \# objects & 50.000 & 243.801 & 3.781.232 & 25.315 & 25.315 \\
    naming vocab size &  5.004 &  10.423 &   105.441 &  1.061 &  7.970 \\
    av. annotations/object &      2.8 &       2.3 &         1.7 &      7.2 &     35.3 \\
    \% objects with n types $>$ 1 &      0.7 &       0.3 &         0.02 &      0.05 &      0.9 \\
    av. types/object &      1.9 &       1.4 &         1 &      1.1 &      5.7 \\
    \bottomrule
  \end{tabular}
  \caption{Overview statistics for different data sets containing object naming data. VGmn shows statistics for the subset of \vg that overlaps with our ManyNames dataset.\label{tab:compare}}
\end{table*}

>>>>

Seminal work by \newcite{rosch1976basic} inspired a taxonomic view of object naming, in which names exhibit a preferred level of specificity or abstraction called the ``entry-level'' \cite{jolicoeur1984pictures}. 
This typically corresponds to an intermediate level of specificity (basic level,\ e.g., \refexp{bird}, \refexp{car}), as opposed to more generic (super-ordinate,\ e.g., \refexp{animal}, \refexp{vehicle}) or more specific categories (sub-ordinate,\ e.g., \refexp{sparrow}, \refexp{convertible}).
However, less prototypical members of basic level categories tend to be instead identified with sub-ordinate categories (e.g., a penguin is typically called \refexp{penguin} and not \refexp{bird}; \newcite{jolicoeur1984pictures}).

%This out-of-context preference towards a certain taxonomic level is often referred to as \textbf{lexical availability}. 
While the traditional notion of entry-level categories suggests that objects tend to be named by a \refexp{single} preferred concept, research on pragmatics has found that speakers adopt their naming choices to the context and, hence, are flexible with respect to the chosen level of specificity \cite{olson1970language,rohde2012communicating,graf2016animal}.
%Scenarios where multiple objects (of the same category) are present induce a pressure for generating names which uniquely identify the target \cite{olson1970language}, such that sub-level names can be systematically elicited in these cases \cite{rohde2012communicating,graf2016animal}.
For example, in presence of more than one dog, the name \textsl{dog} is ambiguous and a sub-ordinate category (e.g., \textsl{rottweiler}, \textsl{beagle}) is potentially preferred by speakers. The effect of such distractor objects on the production of referring expressions has been looked at a lot in the language generation community \cite{krahmer:2012}, though not specifically for object naming. We believe that our new dataset provides an interesting resource for tackling this question.
%, though additional factors such as cost or saliency also come into play \cite{graf2016animal,clark1983common}.

The purely taxonomic view on naming has also been criticized in more recent work on object organization, which found that many objects of our daily lifes are part of multiple category systems at the same time \cite{ross1999food,SHAFTO20111}. 
This \textit{cross-classification} occurs, for instance, with food categories which can be taxonomy-based (e.g.\ \refexp{meat, vegetable}) or script-based (e.g.\  \refexp{breakfast, snack}).
We provide tentative evidence that cross-classification is indeed relevant for naming variation, and that the taxonomic axis is not the main parameter that accounts for variation in our data.

@@

\begin{table*}[htb]
  \centering
  \begin{tabular}{lrrrrr}
    \toprule
    &   RefCOCO/+  &  Flickr30kE &           VG &      VGmn &        MN \\
    \midrule
    \# objects & 50.000 & 243.801 & 3.781.232 & 25.315 & 25.315 \\
    naming vocab size &  5.004 &  10.423 &   105.441 &  1.061 &  7.970 \\
    av. annotations/object &      2.8 &       2.3 &         1.7 &      7.2 &     35.3 \\
    \% objects with n types $>$ 1 &      0.7 &       0.3 &         0.02 &      0.05 &      0.9 \\
    av. types/object &      1.9 &       1.4 &         1 &      1.1 &      5.7 \\
    \bottomrule
  \end{tabular}
  \caption{Overview statistics for different data sets containing object naming data. VGmn shows statistics for the subset of \vg that overlaps with our ManyNames dataset.\label{tab:compare}}
\end{table*}

### 2019-11-29 papers/LREC2020/data-collection.tex
more discussion in sec 3

We take data from \vgenome~(VG, \newcite{krishna2016visualgenome}), which
contains a dense region-based labeling of $108$K~images with, inter alia, object names, attributes and relationships,
all linked to WordNet synsets \cite{fellbaum1998wordnet}.
\vg suits our purpose of collecting names for naturalistic instances of common objects, as it has images of varying complexity, with close-ups as well as images with many objects.
As common in Computer Vision, objects are localized as bounding boxes, as in Figure~\ref{fig:cake}.% 
\footnote{We use image and object interchangeably in the following, since we only selected one target object per image (i.e., each object and image in VG is chosen at most once).}

>>>>

\sz{the next paragraph is quite redundant, isn't it?}
We take data from VG \cite{krishna2016visualgenome}, which
contains a dense region-based labeling of $108$K~images with, inter alia, object names, attributes and relationships,
all linked to WordNet synsets \cite{fellbaum1998wordnet}.
\vg suits our purpose of collecting names for naturalistic instances of common objects, as it has images of varying complexity, with close-ups as well as images with many objects.
As common in Computer Vision, objects are localized as bounding boxes, as in Figure~\ref{fig:cake}.% 
\footnote{We use image and object interchangeably in the following, since we only selected one target object per image (i.e., each object and image in VG is chosen at most once).}

### 2019-11-29 papers/LREC2020/intro.tex
more discussion in sec 3

Compared to work on perception and language grounding in Linguistics or Cognitive Science, however, recent data collections in L\&V capture a rather limited amount of inter-speaker variation.
For instance, so-called picture naming norms used in Psycholinguistics record naming responses for hundreds of speakers for the same object  \cite{snodgrass,rossion2004revisiting}, whereas captioning or referring expression data sets typically provide less than 10 annotations per entity \cite{devlin:imcaqui,Kazemzadeh2014,mao15}.
Consequently, a reliable assessment of inter-annotator agreement, speaker preferences, and a deeper linguistic analysis of the observed variation is mostly not possible with available data collections in  L\&V.
At the same time, these datasets have much potential for research on these topics, as they provide more realistic images of real-world objects and scenes than the idealized drawings used in picture naming norms (see Figure \ref{fig:cake}), as well as a wider coverage of object categories.
A more systematic understanding of the factors influencing the choice of object names could inform theoretical work on language grounding and pragmatics \cite{rohde2012communicating,graf2016animal}, as well as the design of models and architectures in L\&V \cite{lazaridou-dinu-baroni:2015:ACL-IJCNLP,Ordonez:2016,zhao2017open}.

@@

The trends we identify in the dataset are illustrated in Figure \ref{fig:cake} (left): Our data reveals clear naming preferences (in the example, 53\% of the annotators prefer the so-called basic-level name \textit{cake}, see Section \ref{subsec:rosch} for further explananation) and also rich variation (the remaining annotators prefer other options like \textit{food, dessert, bread}) that is not restricted to taxonomic relations studied in previous work on naming \cite{Ordonez:2016,graf2016animal}: while \word{food} is in a taxonomic relation to \word{cake} (it is a hypernym), \textit{dessert} highlights a different facet of the object.

>>>>

Compared to work on perception and language grounding in Linguistics or Cognitive Science, however, recent data collections in L\&V capture a rather limited amount of inter-speaker variation.
For instance, so-called picture naming norms used in Psycholinguistics record naming responses for hundreds of speakers for the same object  \cite{snodgrass,rossion2004revisiting}, whereas captioning or referring expression data sets typically provide less than 10 annotations per entity \cite{devlin:imcaqui,Kazemzadeh2014,mao15}.
Consequently, a reliable assessment of inter-annotator agreement, speaker preferences, and a deeper linguistic analysis of the observed variation is mostly not possible with available data collections in  L\&V.
At the same time, these datasets have much potential for research on these topics, as they provide more realistic images of real-world objects and scenes than the idealized drawings used in picture naming norms (see Figure \ref{fig:cake}), as well as a wider coverage of object categories.
A more systematic understanding of the factors influencing the choice of object names could inform theoretical work on language grounding and pragmatics \cite{rohde2012communicating,graf2016animal}, as well as the design of models and architectures in L\&V, along the lines of e.g.\ \cite{lazaridou-dinu-baroni:2015:ACL-IJCNLP,Ordonez:2016,zhao2017open}.

@@

The trends we identify in the dataset are illustrated in Figure \ref{fig:cake} (left): Our data reveals clear naming preferences (in the example, 53\% of the annotators prefer the so-called basic-level name \textit{cake}, see Section \ref{subsec:rosch} for further explanation) and also rich variation (the remaining annotators prefer other options like \textit{food, dessert, bread}) that is not restricted to taxonomic relations studied in previous work on naming \cite{Ordonez:2016,graf2016animal}: while \word{food} is in a taxonomic relation to \word{cake} (it is a hypernym), \textit{dessert} highlights a different facet of the object.

### 2019-11-29 papers/LREC2020/survey.tex
more discussion in sec 3

%\cs{If space allows, I would also put an example image+annotation for RefCOCO and Flickr30kE}
%\gbt{Space doesn't seem to allow :)}
We identified three previously existing resources that can be of use for analysis and modeling of object naming: RefCOCO (and a variant, RefCOCO+), Flickr30k Entities, and Visual Genome. %
%\footnote{Other resources, such as \gbt{imagenet, openimages, see the other datasets cited in the openimages dataset}, provide object categories, rather than names.}
% footnote not necessary! this is explained in the background section
Table~\ref{tab:compare} summarizes their main characteristics and compares them to our dataset (last two columns; see Section~\ref{sec:data}).
As the table shows, previous datasets provide between one and three annotations per object, which, we believe, is not enough to assess naming behavior for individual objects.
This motivates our data collection. %, in which we collect 36 names per object.
Since these datasets can, however, be useful to examine other aspects of object naming, we summarize their characteristics below.

@@

We expect this dataset to be good to examine the effect of context on naming choices in a referential setting, because the images contain complex scenes with other objects of more or less similar categories, i.e.\ so-called distractors \cite{krahmer:2012}.
Moreover, multiple annotations ($2.84$\ on average) allow for some minimal analysis of naming preferences and variation.
However, note that not all objects of an image are annotated with REs and corresponding categories, so it may be difficult to analyze the effect of distractors with automatic processing.
Also, while in \refcoco the elicited names can assumed to be natural, it is unclear how the additional constraints in \refcocop impact on the naturalness of object naming.
Finally, the main drawback of this dataset is that the set of categories included is quite small ($80$~COCO categories).
To sum up, we would recommend \refcoco to study the effect of distractors on object naming in a restricted set of categories.

@@

One of the main advantages of \vg are its size, with 3.8 million objects as opposed to 50K and 243K for the other two datasets, and its category coverage, with a vocabulary of object names of 105K compared to 5K/10K.
Another is the fact that it in principle provides exhaustive annotations of objects in the image, often with several region descriptions and possibly object names per object.
This should make it easier to identify factors intervening in naming choices, and to model contextual aspects that may affect them, than in the case of \refcoco.
However, there is a crucial pitfall: As Figure \ref{fig:bird} shows, there is only a partial linking of objects that are mentioned across different region descriptions; for instance, the first, second, and fifth object IDs in the figure actually correspond to the same object.
Moreover, the regions for the beak of the object (third and fourth object IDs) overlap with those of the bird.
This means that the identity of objects cannot be established based on the annotation, which severely limits the usefulness of the data to analyze contextual factors for naming.\cs{The explanation of intervening factors in object naming in the background may be a bit more detailed, such as to really understand the drawbacks of the existing datasets with respect to distractors.}

\subsection{Discussion}
\cs{@Sina I changed some stuff here, maybe you prefer the old version...}
As the discussion above showed, while some existing resources can be used to shed light on factors affecting naming choices, they do not provide enough data to assess object-specific naming behavior: To what extent do different people choose the same name for a specific object? How much variation is there? 
To answer these sorts of questions, we need naming data from many subjects for the same objects. 
Also, dense annotations of images can be beneficial to analyze the factors affecting naming (e.g.,\ the category or salience of other objects), and how these impact the modeling of natural language in L\&V.
These are the motivations for our dataset, ManyNames, and for building it on top of \vg, as discussed next.

>>>>

%\cs{If space allows, I would also put an example image+annotation for RefCOCO and Flickr30kE}
%\gbt{Space doesn't seem to allow :)}
We identified three previously existing resources that can be of use for analysis and modeling of object naming: RefCOCO (and a variant, RefCOCO+), Flickr30k Entities, and Visual Genome. %
Table~\ref{tab:compare} summarizes their main characteristics and compares them to our dataset (last two columns; see Section~\ref{sec:data}).
As the table shows, previous datasets provide between one and three annotations per object, which, we believe, is not enough to assess naming behavior for individual objects and which
motivates our data collection. %, in which we collect 36 names per object.
In the following, we will look at their characteristics in more detail and work out requirements for a dataset that is suitable below for a large-scale, in-depth study targeted at object naming.

@@

The statistics in Table \ref{tab:compare} suggest that the multiple annotations ($2.84$\ on average) actually contain a considerable amount of variation in naming (almost 2 different names on average per object). However, the small number of annotations per object would not allow for a reliable assessment of speaker agreement.

RefCOCO has been used to model and examine the effect of context on referring expression generation in general \cite{Yu2016}, though this work did not look at object names specifically. 
A controlled analysis of the effect of context on choice in object naming, as for instance in \cite{graf2016animal}, would require substantial further data annotation as not all objects of an image are annotated with REs and corresponding categories. Hence, so-called distractor objects  \cite{krahmer:2012} and their names cannot be analyzed systematically.
Also, while in \refcoco the elicited names can assumed to be natural, it is unclear how the additional constraints in \refcocop impact on the naturalness of object naming.
Finally, the main drawback of this dataset is that the set of categories included is quite small ($80$~COCO categories).
To sum up, \refcoco is suitable for generally modeling referring expressions in context for a restricted set of categories, but less appropriate for analyzing object naming in particular.

@@

One of the main advantages of \vg are its size, with 3.8 million objects as opposed to 50K and 243K for the other two datasets, and its category coverage, with a vocabulary of object names of 105K compared to 5K/10K.
Another is the fact that it, in principle, provides exhaustive annotations of objects in the image, often with several region descriptions and possibly object names per object.
This should make it easier to identify factors intervening in naming choices, and to model contextual aspects that may affect them, than in the case of \refcoco.

However, there is a crucial pitfall: As Figure \ref{fig:bird} shows, there is only a partial linking of objects that are mentioned across different region descriptions; for instance, the first, second, and fifth object IDs in the figure actually correspond to the same object.
Moreover, the regions for the beak of the object (third and fourth object IDs) overlap with those of the bird.
This means that the identity of objects cannot be established based on the annotation, which severely limits the usefulness of the data to analyze naming.
The relatively low number of annotations per objects in VisualGenome (1.7 on average) shown in Table \ref{tab:compare} and the very small number of objects that have more than one name associated with it (5\%) seem to be an effect of this problem.
Thus, even though there is a different name (\textit{vulture}) for \textit{bird} object in Figure \ref{fig:bird}, this cannot be established based on the given data.
We experimented with filtering and merging bounding boxes based on overlap, but this would introduce substantial noise into the data (e.g.\ truly overlapping objects).

Table \ref{tab:compare} also shows the statistics for the subset of objects that we selected for ManyNames and, here, we find a considerably higher average of annotations per object (7). However, interestingly, the portion of objects that have different names associated with them is still extremely small.
Note that, even though RefCOCO has much less annotations per object, there are many objects with different names (70\%).

%\cs{The explanation of intervening factors in object naming in the background may be a bit more detailed, such as to really understand the drawbacks of the existing datasets with respect to distractors.}

\subsection{Discussion}
\cs{@Sina I changed some stuff here, maybe you prefer the old version...}
As the discussion above showed, while some existing resources can be used to shed light on factors affecting naming choices, they do not provide enough data to systematically assess how variable object naming really is. The RefCOCO data suggest that many objects  object-specific naming behavior: To what extent do different people choose the same name for a specific object? How much variation is there? 
To answer these sorts of questions, we need naming data from many subjects for the same objects. 
Also, dense annotations of images can be beneficial to analyze the factors affecting naming (e.g.,\ the category or salience of other objects), and how these impact the modeling of natural language in L\&V.
These are the motivations for our dataset, ManyNames, and for building it on top of \vg, as discussed next.
